---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# posteriors3 

[![Appveyor Build status](https://ci.appveyor.com/api/projects/status/99jojhgk9t4agdmv/branch/main?svg=true)](https://ci.appveyor.com/project/paulnorthrop/posteriors3/branch/main)
[![R-CMD-check](https://github.com/paulnorthrop/posteriors3/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/paulnorthrop/posteriors3/actions/workflows/R-CMD-check.yaml)
[![Coverage Status](https://codecov.io/github/paulnorthrop/posteriors3/coverage.svg?branch=master)](https://app.codecov.io/github/paulnorthrop/posteriors3?branch=master)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/posteriors3)](https://cran.r-project.org/package=posteriors3)
[![Downloads (monthly)](https://cranlogs.r-pkg.org/badges/posteriors3?color=brightgreen)](https://cran.r-project.org/package=posteriors3)
[![Downloads (total)](https://cranlogs.r-pkg.org/badges/grand-total/posteriors3?color=brightgreen)](https://cran.r-project.org/package=posteriors3)

## Univariate Bayesian Analyses using S3 Probability Distribution Objects

Provides functions to perform univariate Bayesian analyses using the S3 probability distribution objects provided by the [distributions3](https://cran.r-project.org/package=distributions3) package. A multiplication generic function is provided so that a posterior distribution object can be created from a product of a likelihood object and a prior distribution object. If a conjugate prior is used then the posterior distribution object is also an S3 probability distribution object. 

## An example

We perform a univariate Bayesian analysis based on a random sample from a Binomial distribution using a conjugate Beta prior distribution for the probability $p$.

```{r, echo = FALSE}
set.seed(7122024)
```

```{r, message = FALSE, warning = FALSE}
library(distributions3)
library(posteriors3)

# Create a Binomial(5, 0.2) distribution object
N <- Binomial(size = 5, 0.2)
N

# Draw a random sample of size 10 from this distribution
data <- random(N, n = 10)
data

# Add the data to the object N as an attribute "data"
likelihood <- add_data(N, data)
attr(likelihood, "data")

# Set a conjugate (Jeffreys) prior distribution
prior <- Beta(alpha = 1 / 2, beta = 1 / 2)
prior

# The posterior distribution is proportional to likelihood * prior
posterior <- likelihood * prior
posterior
```

This agrees with the result that the posterior is a Beta distribution with parameters $\alpha + \sum_{i=1}^n x_i$ and $\beta + \sum_{i=1}^n (5 - x_i)$, where here $\alpha = \beta = 1/2$ and $(x_1, ..., x_{10}) = (`r paste(data, collapse = ",")`)$.

## Installation

To get the current released version from CRAN:

```{r installation, eval = FALSE}
install.packages("posteriors3")
```
